# Statistical Inference Course Project (Part 2)
## Title: Analyze the ToothGrowth data
### Overview
#### In this project we use the ToothGrowth data and provide a basic summary. We also use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose and describe a colclusion.

### Question 1: Load the ToothGrowth data and perform some basic exploratory data analyses.
Loading the data and viewing a few rows

```{r}
library(datasets)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
```
Perform some basic exploratory data analyses

```{r}
library(ggplot2)

ggplot(ToothGrowth, aes(x=factor(dose), y=len, fill=factor(dose))) +
        ggtitle("Perform Exploratory Analysis of the ToothGrowth Dataset") +
        geom_boxplot(notch=F) +
        facet_grid(.~supp, margins = FALSE, scales = "fixed", space = "fixed") +
        scale_x_discrete("Dose") +   
        scale_y_continuous("Teeth Length")
```

### Question 2: Provide a basic summary of the data.
```{r}
summary(ToothGrowth)

table(ToothGrowth$dose, ToothGrowth$supp)

```
### Question 3: Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

```{r}
hypo_test_1 <- t.test(len~supp, paired=FALSE, var.equal=TRUE, data=ToothGrowth)
hypo_test_2 <- t.test(len~supp, paired=FALSE, var.equal=FALSE, data=ToothGrowth)

hypo_test_result <- data.frame("p-value"=c(hypo_test_1$p.value, hypo_test_2$p.value),
                          "Lower_Conf_Limit"=c(hypo_test_1$conf[1],hypo_test_2$conf[1]),
                          "Higher_Conf_Limit"=c(hypo_test_1$conf[2],hypo_test_2$conf[2]),
                          row.names=c("Equal Variance","Unequal Variance"))

hypo_test_result

```

### Question 4: State your conclusions and the assumptions needed for your conclusions.

1.  Orange juice and Vitamin C have different effects on tooth growth.

2. Dosage is a key factor in tooth growth, regardless of the supplement methods.

3. Larger dosages have greater impact on tooth growth (2 mg dosage has the highest impact on tooth growth, then 1 mg. 0.5mg dosage has the lowest impact on tooth growth.

4. At a higher dosage level (2 mg), the tooth growth rate is not statistically significant for different supplement methods.